---
title: "Measures Taken Formal Musical Analysis"
author: "Noah Zeldin"
date: "4/26/2021"
output: github_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
knitr::opts_knit$set(root.dir = "C:/Users/Noah Zeldin/Desktop/Proposal/R materials for dissertation/data/Massnahme_data")
```

# Load packages  

```{r}
library(tidyverse)
library(readxl)
library(ggforce)
library(scales)
library(lubridate)
library(mosaic) # may be unnecessary
```

# Importation

## Duration

1. Import all sheets into a single list and specify column types.  

```{r}
durations_sheets <- excel_sheets("Massnahme_durations_meter_changes.xlsx")

durations_list <- lapply(durations_sheets, 
                         function(x) 
                             read_excel("Massnahme_durations_meter_changes.xlsx", 
                                                  sheet = x, 
                                                          col_types = c(
                                                              "text", # piece_no
                                                              "numeric", # category
                                                              "text", # subcategory
                                                              "numeric", # segment
                                                              "numeric", # m_start
                                                              "numeric", # m_end
                                                              "numeric", # no_of_mm
                                                              "numeric", # meter_1
                                                              "numeric", # meter_2
                                                              "numeric", # meter_ch_count
                                                              "numeric", # quarters_per_bar
                                                              "numeric", # beats
                                                              "numeric", # tempo
                                                              "numeric", # tempo_ch_count
                                                              "numeric") # duration
                                                          ))
```

2. From list create single data frame and save as tibble.

```{r}
dur_tib <- as_tibble(bind_rows(durations_list))
```

## Importation - Voice Analysis

1. Check worksheets.

* ensure that there is a sheet for each choral piece

```{r}
excel_sheets("Massnahme_choir_voice_analysis.xlsx")
```

2. Import all sheets into a single list and specify column types.

```{r}
voice_analysis_sheets <- excel_sheets("Massnahme_choir_voice_analysis.xlsx")

voice_analysis_list <- lapply(voice_analysis_sheets, 
                           function(x) read_excel("Massnahme_choir_voice_analysis.xlsx", 
                                                  sheet = x, 
                                                          col_types = c(
                                                              "text", # piece_no
                                                              "numeric", # measure
                                                              "text", # texture
                                                              "numeric", # voices
                                                              "text", # groupings
                                                              
                                                              "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", # soprano:ratio
                                                              
                                                              "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", # rests
                                                              
                                                              "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", # quarters
                                                              
                                                              "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", # notes
                                                              
                                                              "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", "text", "numeric", # tones
                                                              
                                                              "numeric", "numeric", # spoken, acapella
                                                              
                                                              "numeric", "numeric", "numeric", "numeric", # meter etc.
                                                              
                                                              "numeric", "numeric", "numeric", "numeric", # general dur's
                                                              
                                                              "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", "numeric" # dur's of voices
                                                              ) 
                                                              ))
```


3. From list create single data frame and save as tibble.

```{r}
gen_tib <- as_tibble(bind_rows(voice_analysis_list))
```



# Cleaning and Manipulation

## General Refinement 

### Durations

Convert **piece_no**, **category** and **subcategory** to factors.

```{r}
dur_tib <- dur_tib %>% 
    mutate(piece_no = as_factor(piece_no)) %>% 
    mutate(category = as_factor(category)) %>% 
    mutate(subcategory = as_factor(subcategory))
```

<!-- Check to see if each piece is now a factor. -->

<!-- * NB: n col. refers to # of segments -->

<!-- ```{r} -->
<!-- dur_tib$piece_no %>%  -->
<!--     fct_count() -->
<!-- ``` -->

<!-- same for category -->

<!-- ```{r} -->
<!-- dur_tib$category %>%  -->
<!--     fct_count() -->
<!-- ``` -->


Relevel subcategories.

```{r}
dur_tib$subcategory <- dur_tib$subcategory %>% 
    fct_relevel("1b", after = 1) %>% 
    fct_relevel("2b", after = 2) %>% 
    fct_relevel("3b", after = 4) %>% 
    fct_relevel("3c", after = 5)

dur_tib$subcategory %>% 
    fct_count()
```

### Voice Analysis


## Create gen_tib

Convert **piece_no** to factor.

```{r}
gen_tib <- gen_tib %>% 
    mutate(piece_no = as_factor(piece_no))
```

<!-- Check to see if each piece is now a factor. -->
<!-- * **Add something about n = # of mm. - and check.** -->

<!-- ```{r} -->
<!-- gen_tib$piece_no %>%  -->
<!--     fct_count() -->
<!-- ``` -->

Since 6c now follows 7a, must relevel (and check).

```{r}
gen_tib$piece_no <- gen_tib$piece_no %>% 
    fct_relevel("6c", after = 7)

gen_tib$piece_no %>% 
    fct_count()
```

Group by piece.

```{r}
by_piece <- gen_tib %>% group_by(piece_no)
```

Add **rowid** column and make first column (called "id").

```{r}
gen_tib <- gen_tib %>% 
    rowid_to_column("id")
```


### Additional Calculations for Density

translate texture to numeric value in new column
* monophony = 1
* homophony = 1.5
* antiphony = 1.5
* polyphony = 2

```{r}
gen_tib <- gen_tib %>% 
    mutate(texture_value = case_when(texture == "na" ~ "0", 
                                   texture == "m" ~ "1", 
                                   texture == "h" ~ "1.5", 
                                   texture == "a" ~ "1.5", # added 12.26.20
                                   texture == "p" ~ "2",)) %>% 
    mutate(texture_value = as.numeric(texture_value)) %>% 
    relocate(texture_value, .after = texture)
```

add density column for each voice

```{r}
gen_tib <- gen_tib %>% 
    mutate(dm_s1 = (notes_s1+tones_s1)/quarters_per_bar,
                      dm_s2 = (notes_s2+tones_s2)/quarters_per_bar,
                      dm_a1 = (notes_a1+tones_a1)/quarters_per_bar,
                      dm_a2 = (notes_a2+tones_a2)/quarters_per_bar,
                      dm_t1 = (notes_t1+tones_t1)/quarters_per_bar,
                      dm_t2 = (notes_t2+tones_t2)/quarters_per_bar,
                      dm_b1 = (notes_b1+tones_b1)/quarters_per_bar,
                      dm_b2 = (notes_b2+tones_b2)/quarters_per_bar)
```

create a **dm_sum** column from 8 individual **dm** columns

```{r}
gen_tib <- gen_tib %>% 
    rowwise() %>% 
    mutate(dm_sum = sum(c_across(dm_s1:dm_b2)))
```

With new **dm_sum** column, create **dmc** column.

```{r}
gen_tib <- gen_tib %>% 
    rowwise() %>% 
    mutate(dmc = (dm_sum/4)*texture_value)
```

Need to reconvert gen_tib to tibble after performing rowwise()

```{r}
gen_tib <- gen_tib %>% as_tibble()
```


### Create gen_tib_sung

1. Filter out parts without choral singing. (This includes passages spoken by
the choir.)
* **CHECK IF NECESSARY TO ADD** `as_tibble()` **TO END.**

```{r}
gen_tib_sung <- gen_tib %>% 
    filter(texture != "na" & 
               parts_active > 0 & 
               spoken == 0) %>% 
    as_tibble() # may not be necessary
```

2. Check to see if any NAs remain. The following should return an **empty** 
table.

```{r}
gen_tib_sung %>% 
    filter(is.na(dm_s1),
           is.na(dm_s2), 
           is.na(dm_a1),
           is.na(dm_a2),
           is.na(dm_t1),
           is.na(dm_t2),
           is.na(dm_b1),
           is.na(dm_b2)) %>% 
    select(id, piece_no, measure, starts_with("notes_"), starts_with("tones_"),
           quarters_per_bar, starts_with("dm_")) 
```


### Create pitch_tib

```{r}
pitch_tib <- gen_tib_sung %>% 
    select(id, piece_no, measure, tones, dur_choir, dmc) %>%
    relocate(tones, .after = dmc) %>% 
    mutate(
        c = str_count(tones, "c$|c\\,"),
        c_sharp_d_flat = str_count(tones, "c-sharp|d-flat"),
        d = str_count(tones, "d$|d\\,"),
        d_sharp_e_flat = str_count(tones, "d-sharp|e-flat"),
        e = str_count(tones, "e$|e\\,"),
        f = str_count(tones, "f$|f\\,"),
        f_sharp_g_flat = str_count(tones, "f-sharp|g-flat"),
        g = str_count(tones, "g$|g\\,"),
        g_sharp_a_flat = str_count(tones, "g-sharp|a-flat"),
        a = str_count(tones, "a$|a\\,"),
        a_sharp_b_flat = str_count(tones, "a-sharp|b-flat"),
        b = str_count(tones, "b$|b\\,"),    
                ) %>% 
    rowwise %>% 
    mutate(tones_sum = sum(c_across(c:b))) 
```

