---
title: "Measures Taken Formal Musical Analysis"
author: "Noah Zeldin"
date: "4/26/2021"
output: github_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
knitr::opts_knit$set(root.dir = "C:/Users/Noah Zeldin/Desktop/Proposal/R materials for dissertation/data/Massnahme_data")
```

# Preliminary Set-up

Load packages  

```{r}
library(tidyverse)
library(readxl)
library(ggforce)
library(scales)
library(lubridate)
library(mosaic) # may be unnecessary
```

# Importation

## Importation - Duration

check worksheets
* ensure that there is a sheet for each piece except 2a; should be 21

```{r}
excel_sheets("Massnahme_durations_meter_changes.xlsx")
```

import all sheets into a single list and specify column types  

```{r}
durations_sheets <- excel_sheets("Massnahme_durations_meter_changes.xlsx")

durations_list <- lapply(durations_sheets, 
                         function(x) 
                             read_excel("Massnahme_durations_meter_changes.xlsx", 
                                                  sheet = x, 
                                                          col_types = c(
                                                              "text", # piece_no
                                                              "numeric", # category
                                                              "text", # subcategory
                                                              "numeric", # segment
                                                              "numeric", # m_start
                                                              "numeric", # m_end
                                                              "numeric", # no_of_mm
                                                              "numeric", # meter_1
                                                              "numeric", # meter_2
                                                              "numeric", # meter_ch_count
                                                              "numeric", # quarters_per_bar
                                                              "numeric", # beats
                                                              "numeric", # tempo
                                                              "numeric", # tempo_ch_count
                                                              "numeric") # duration
                                                          ))
```

from list create single data frame and save as tibble

* can probably combine into single command

```{r}
dur_df <- bind_rows(durations_list)

dur_tib <- as_tibble(dur_df)
```

## Importation - Voice Analysis

check worksheets
* ensure that there is a sheet for each choral piece

```{r}
excel_sheets("Massnahme_choir_voice_analysis.xlsx")
```

import all sheets into a single list and specify column types

```{r}
voice_analysis_sheets <- excel_sheets("Massnahme_choir_voice_analysis.xlsx")

voice_analysis_list <- lapply(voice_analysis_sheets, 
                           function(x) read_excel("Massnahme_choir_voice_analysis.xlsx", 
                                                  sheet = x, 
                                                          col_types = c(
                                                              "text", # piece_no
                                                              "numeric", # measure
                                                              "text", # texture
                                                              "numeric", # voices
                                                              "text", # groupings
                                                              
                                                              "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", # soprano:ratio
                                                              
                                                              "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", # rests
                                                              
                                                              "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", # quarters
                                                              
                                                              "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", # notes
                                                              
                                                              "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", "text", "numeric", # tones
                                                              
                                                              "numeric", "numeric", # spoken, acapella
                                                              
                                                              "numeric", "numeric", "numeric", "numeric", # meter etc.
                                                              
                                                              "numeric", "numeric", "numeric", "numeric", # general dur's
                                                              
                                                              "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", "numeric" # dur's of voices
                                                              ) 
                                                              ))
```


from list create single data frame and save as tibble

* again, probably combine into single command

```{r}
gen_df <- bind_rows(voice_analysis_list)

gen_tib <- as_tibble(gen_df)
```

