---
title: The Reception of The Measures Taken and The Mother in the Political-Aesthetic
  Space of the Weimar Republic
author: "Noah Zeldin"
date: "4/27/2021"
output: 
  github_document:
    toc: true
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
knitr::opts_knit$set(root.dir = "C:/Users/Noah Zeldin/Desktop/Proposal/R materials for dissertation/data")
```

# Introductory Remarks

Below is the annotated set-up for my quantitative analysis of the Weimar-era 
reception of Brecht and Eisler's *The Measures Taken* and *The Mother*, which is included in the second chapter of my dissertation. This analysis was conducted in R. (I have tried to use [tidyverse](https://www.tidyverse.org/) syntax as 
consistently as possible.) Data sets will be made available to researchers upon 
request.

**NB: Further refinements to the coding are forthcoming.** 

# Load Packages

```{r}
library(tidyverse)
library(readxl)
library(quanteda)
library(quanteda.textmodels)
library(readtext)
library(tidytext)
library(ggplot2)
library(scales)
library(igraph)
library(ggraph)
library(FactoMineR)
library(RColorBrewer)
library(lubridate)
```

# Importation

NB: Several articles had to be removed because of their distortionary effects.
This resulted in multiple versions of the data, as shown below. (This will be 
cleaned up in the near future.)

Main Spreadsheet

```{r}
spreadsheet <- read_excel("all_documents_updated_9.10.xlsx", sheet = "All")
```

Spreadsheet w/o Massnahme Erfurt

```{r}
spreadsheet_no_erfurt <- spreadsheet[-(c(38:45, 49)),]
```

Spreadshet w/or Massnahme Erfurt or "Kartenhaus"

```{r}
spreadsheet_reduced <- spreadsheet[-(c(38:45, 49, 65)),]
```




