---
title: The Reception of The Measures Taken and The Mother in the Political-Aesthetic
  Space of the Weimar Republic
author: "Noah Zeldin"
date: "4/27/2021"
output: 
  github_document:
    toc: true
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
knitr::opts_knit$set(root.dir = "C:/Users/Noah Zeldin/Desktop/Proposal/R materials for dissertation/data")
```

# Introductory Remarks

Below is the annotated set-up for my quantitative analysis of the Weimar-era 
reception of Brecht and Eisler's *The Measures Taken* and *The Mother*, which is 
included in the second chapter of my dissertation. This analysis was conducted 
in R and relies heavily on the [quanteda](https://quanteda.io/) package (for 
general manipulation, word counts, etc.) and
[FactoMineR](http://factominer.free.fr/index.html) package (for correspondence 
analysis). (Also, I have tried to use [tidyverse](https://www.tidyverse.org/) 
syntax as consistently as possible.) Data sets will be made available to 
researchers upon request.

**NB: Further refinements to the coding are forthcoming.** This was my first 
serious attempt at coding in R, so certain portions are still a bit clunky. 
(Note too that many lines use the German titles for the two pieces. All 
instances of this will be changed to English for consistency.)

# Load Packages

```{r}
library(tidyverse)
library(readxl)
library(quanteda)
library(quanteda.textmodels)
library(readtext)
library(tidytext)
library(ggplot2)
library(scales)
library(igraph)
library(ggraph)
library(FactoMineR)
library(RColorBrewer)
library(lubridate)
```

# Importation

NB: Several articles had to be removed because of their distortionary effects.
This resulted in multiple versions of the data, as shown below. (This will be 
cleaned up in the near future.)

Main Spreadsheet

```{r}
spreadsheet <- read_excel("all_documents_updated_9.10.xlsx", sheet = "All")
```

Spreadsheet w/o Massnahme Erfurt

```{r}
spreadsheet_no_erfurt <- spreadsheet[-(c(38:45, 49)),]
```

Spreadshet w/or Massnahme Erfurt or "Kartenhaus"

```{r}
spreadsheet_reduced <- spreadsheet[-(c(38:45, 49, 65)),]
```

# Quanteda Set-Up

## Create Corpora

### General Corpora

General Corpus

```{r}
corp <- corpus(spreadsheet, text_field = "Text")
```

General Corpus w/o Massnahme Erfurt

```{r}
corp_no_erfurt <- corpus(spreadsheet_no_erfurt, text_field = "Text")
```

General Corpus Reduced

```{r}
corp_reduced <- corpus(spreadsheet_reduced, text_field = "Text")
```

### Piece Corpora

Massnahme Corpus

```{r}
mass_corp <- corpus_subset(corp, Piece == "Massnahme")
```

Massnahme Corpus No Erfurt

```{r}
mass_corp_no_erfurt <- corpus_subset(corp_no_erfurt, Piece == "Massnahme")
```

Mutter Corpus

```{r}
mutter_corp <- corpus_subset(corp, Piece == "Mutter")
```

### Title Corpora - NO MASSNAHME YET

Title Corpus

```{r}
corp_title <- corpus(spreadsheet, text_field = "Title")
```

Mutter Title Corpus

```{r}
mutter_corp_title <- corpus_subset(corp_title, Piece == "Mutter")
```

## Corpus Summary - Article Lengths, etc.

```{r}
corp_reduced_summary <- textstat_summary(corp_reduced) %>% 
  as_tibble

corp_reduced_summary$document <- corp_reduced_summary$document %>% 
        str_replace("text", "") 
    
corp_reduced_summary <- corp_reduced_summary %>% mutate(document = as.numeric(document)) %>% 
        rename(Article = document) %>% # this seems to work better than including in above step
        left_join(spreadsheet, by = "Article") %>% 
        select(-c(Text, Other_Metadata:Comp_Doc))
```


## Dictionaries and Additional Stopwords

General Dictionary

```{r}
dict_gen <- dictionary(list(revolution = "revolution*",
                            bertolt = c("bert*", "bertolt*"),
                            theater = c("theater*", "theatralisch*"),
                            episch = "episch*",
                            musik = "musik*",
                            drama = "drama*",
                            politisch = "politi*",
                            kommunismus = "kommunis*",
                            chor = c("chor*", "chöre*"), 
                            proletarisch = "prolet*",
                            marxismus = "marx*",
                            primitiv = "primitiv*",
                            lehrstück = "lehrstück*",
                            brecht = "brecht*",
                            eisler = "eisler*",
                            gorki = "gorki*",
                            bürgerlich = "bürgerlich*",
                            propaganda = "propagand*",
                            kunst = c("kunst", "künstler*"),
                            lied = c("lied*", "song*"),
                            arbeitersänger = "arbeitersänger*", 
                            arbeiterchor = "arbeiterch*", 
                            bolschewismus = c("bolschewis*",
                                              "kulturbolschewis*"), 
                            langweilig = c("langweilig*", 
                                           "langeweile")))
```

Regex Dictionary

```{r}
dict_regex <- dictionary(list(lehrlern = c("lehr(?!s)[a-z]+", 
                                           "belehr(?!s)[a-z]+", 
                                           "lern[a-z]+",
                                           "erlern[a-z]+", 
                                           "gelern[a-z]+", 
                                           "pädagog[a-z]+", 
                                           "didakt[a-z]+"))) 
```

Additional Stopwords

```{r}
sw_add <- c("dass", "wurde", "schon", "mehr", "ganz*", "immer", "gibt", "ja",
            "müssen", "kommt", "sei", "tun")
```

## Tokenize and Filter Corpora

Create function for tokenizing and removing stopwords:

```{r}
tokenize_and_remove_stopwords <- function(i) {
    tokens(i,
           remove_punct = TRUE,
           remove_numbers = TRUE,
           remove_symbols = TRUE) %>% 
        tokens_remove(c(stopwords("de"), sw_add)) %>% 
        tokens_remove(valuetype = "regex", "[0-9]+") %>% 
        tokens_keep(min_nchar = 3) 
}
```

Tokenize and filter corpora:

```{r}
# general / ungrouped
gen_toks <- tokenize_and_remove_stopwords(corp)
# general / ungrouped NO ERFURT
gen_toks_no_erfurt <- tokenize_and_remove_stopwords(corp_no_erfurt)
# general / ungrouped REDUCED
gen_toks_reduced <- tokenize_and_remove_stopwords(corp_reduced)
# Massnahme
mass_toks <- tokenize_and_remove_stopwords(mass_corp)
# Massnahme NO ERFURT
mass_toks_no_erfurt <- tokenize_and_remove_stopwords(mass_corp_no_erfurt)
# Mutter
mutter_toks <- tokenize_and_remove_stopwords(mutter_corp)
# ADDITION 12.17.20 - Mutter TITLE
mutter_title_toks <- tokenize_and_remove_stopwords(mutter_corp_title)
```

## DFMs

Create function for converting toks to dfm and applying dictionaries:

```{r}
convert_to_dfm_and_apply_dictionaries <- function(i) {
    dfm(i) %>% 
        dfm_lookup(dict_gen, exclusive = FALSE) %>% 
        dfm_lookup(dict_regex, valuetype = "regex", exclusive = FALSE)
}
```

Convert and apply dictionaries to corpora:

```{r}
# general / ungrouped
gen_dfm <- convert_to_dfm_and_apply_dictionaries(gen_toks)
# general / ungrouped NO ERFURT
gen_dfm_no_erfurt <- convert_to_dfm_and_apply_dictionaries(gen_toks_no_erfurt)
# general / ungrouped REDUCD
gen_dfm_reduced <- convert_to_dfm_and_apply_dictionaries(gen_toks_reduced)
# Massnahme 
mass_dfm <- convert_to_dfm_and_apply_dictionaries(mass_toks)
# Massnahme NO ERFURT
mass_dfm_no_erfurt <- convert_to_dfm_and_apply_dictionaries(mass_toks_no_erfurt)
# Mutter
mutter_dfm <- convert_to_dfm_and_apply_dictionaries(mutter_toks)
# ADDITION 12.17.20: Mutter TITLE
mutter_title_dfm <- convert_to_dfm_and_apply_dictionaries(mutter_title_toks)
```

### Add GPO to general/ungrouped dfm -

<!-- PROB NEED TO CLEAN UP -->

NB: **GPO** stands for "genearl political orientation."

```{r}
# convert gen_dfm[_reduced] to dataframe
gen_datafr_reduced <- convert(gen_dfm_reduced, to = "data.frame")
# convert corp_reduced to dataframe - this has GPOs + other metadata
corp_reduced_datafr <- convert(corp_reduced, to = "data.frame")


# add GPO column to gen_datafr_reduced
gen_datafr_reduced_gpo <- left_join(gen_datafr_reduced, 
                                    corp_reduced_datafr[ , c("doc_id",    "Generalized_Political_Orientation")], 
                                    by = "doc_id", # 8.01 - now do this
                                    # by = c("document" = "doc_id"), # used to work
                                    copy = TRUE)


# eliminate doc col to perform CA (otherwise 2 quali.sup)
gen_datafr_reduced_gpo_2 <- gen_datafr_reduced_gpo[ , -1]


# ** group dfm's ####

# create grouped dfm: piece.gpo = 8 groups
grouped_dfm <- dfm_group(gen_dfm,
                         groups = c("Piece",
                                    "Generalized_Political_Orientation"))
# same but NO ERFURT
grouped_dfm_no_erfurt <- dfm_group(gen_dfm_no_erfurt,
                                   groups = c("Piece",
                                             "Generalized_Political_Orientation"))
```


### Create GPO grouped dfm's for each piece 

```{r}
# Massnahme
mass_dfm_gpo <- dfm_group(mass_dfm,
                          groups = "Generalized_Political_Orientation")
# Massnahme NO ERFURT
mass_dfm_gpo_no_erfurt <- dfm_group(mass_dfm_no_erfurt,
                                    groups = "Generalized_Political_Orientation")
# Mutter
mutter_dfm_gpo <- dfm_group(mutter_dfm,
                            groups = "Generalized_Political_Orientation")
```

### Less Specific Groupings

```{r}
# by piece
piece_dfm <- dfm_group(gen_dfm,
                       groups = "Piece")
# by GPO
gpo_dfm <- dfm_group(gen_dfm,
                     groups = "Generalized_Political_Orientation")

# less specific groupings NO ERFURT
# by piece
piece_dfm_no_erfurt <- dfm_group(gen_dfm_no_erfurt,
                                 groups = "Piece")
# by GPO
gpo_dfm_no_erfurt <- dfm_group(gen_dfm_no_erfurt,
                               groups = "Generalized_Political_Orientation")
```

### By GPO

```{r}
# Left
left_sub <- dfm_subset(grouped_dfm, 
                       Generalized_Political_Orientation == "Left")
# Right
right_sub <- dfm_subset(grouped_dfm, 
                        Generalized_Political_Orientation == "Right")
# Center
center_sub <- dfm_subset(grouped_dfm, 
                         Generalized_Political_Orientation == "Center")
# Unknown
unknown_sub <- dfm_subset(grouped_dfm,
                          Generalized_Political_Orientation == "Unknown")
```

### By Piece

```{r}
# Massnahme
massnahme_sub <- dfm_subset(grouped_dfm,
                            Piece == "Massnahme")
# Mutter
mutter_sub <- dfm_subset(grouped_dfm,
                         Piece == "Mutter")
```

## Create corpus, dfm, ca, etc. of each piece w/o unknown

<!-- from exp_7.24 -> need to integrate better, just being lazy -->

General - just GPO

```{r}
corp_no_erfurt_or_unknown <- corpus_subset(corp_no_erfurt, 
                                           ! Generalized_Political_Orientation == "Unknown" )

toks_no_erfurt_or_unknown <- tokenize_and_remove_stopwords(corp_no_erfurt_or_unknown)

dfm_no_erfurt_or_unknown <- convert_to_dfm_and_apply_dictionaries(toks_no_erfurt_or_unknown)
```

Just GPO, not piece

```{r}
gpo_dfm_no_erfurt_or_unknown <- dfm_group(dfm_no_erfurt_or_unknown,
                                          groups = "Generalized_Political_Orientation")
```

General - Piece + GPO

```{r}
grouped_dfm_no_erfurt_or_unknown <- dfm_group(dfm_no_erfurt_or_unknown,
                                              groups = c("Piece", "Generalized_Political_Orientation"))
```

Measures Taken

```{r}
mass_corp_no_erfurt_or_unknown <- corpus_subset(corp_no_erfurt, 
                                                Piece == "Massnahme" &! Generalized_Political_Orientation == "Unknown" )


mass_toks_no_erfurt_or_unknown <- tokenize_and_remove_stopwords(mass_corp_no_erfurt_or_unknown)

mass_dfm_no_erfurt_or_unknown <- convert_to_dfm_and_apply_dictionaries(mass_toks_no_erfurt_or_unknown)

mass_dfm_gpo_no_erfurt_or_unknown <- dfm_group(mass_dfm_no_erfurt_or_unknown,
                                               groups = "Generalized_Political_Orientation")
```

Mother

```{r}
mutter_corp_no_unknown <- corpus_subset(corp, 
                                        Piece == "Mutter" &! Generalized_Political_Orientation == "Unknown" )


mutter_toks_no_unknown <- tokenize_and_remove_stopwords(mutter_corp_no_unknown)

mutter_dfm_no_unknown <- convert_to_dfm_and_apply_dictionaries(mutter_toks_no_unknown)

mutter_dfm_gpo_no_unknown <- dfm_group(mutter_dfm_no_unknown,
                                       groups = "Generalized_Political_Orientation")
```


# FactoMineR Set-Up

## Create function for converting dfm to dataframe and performing CA

```{r}
convert_to_dataframe_and_perform_ca <- function(i) {
    convert(i, to = "data.frame") %>% 
        CA(quali.sup = 1, graph = FALSE)
}
```

## Use this function on each dfm

I think this is the only one I need

```{r}
# piece + GPO = 8 groups NO ERFURT OR UNKNOWN
grouped_ca_no_erfurt_or_unknown <- convert_to_dataframe_and_perform_ca(grouped_dfm_no_erfurt_or_unknown)
```

NEW with English - 1.02.21

```{r}
grouped_dfm_no_erfurt_or_unknown_english <- 
  dfm_group(grouped_dfm_no_erfurt_or_unknown,
            groups = c("Measures.Center", "Mother.Center", "Measures.Left",
                       "Mother.Left", "Measures.Right", "Mother.Right"))

grouped_ca_no_erfurt_or_unknown_english <- 
  convert_to_dataframe_and_perform_ca(grouped_dfm_no_erfurt_or_unknown_english)
```



# KWIC and Keyword Exploration

## Create function to link KWIC with data

```{r}
combine_kwic_with_data <- function(corpus, words, window) {
    
    i <- kwic(corpus, words, window = window) %>% 
        as_tibble() 
    
    i$docname <- i$docname %>% 
        str_replace("text", "") 
    
    i <- i %>% mutate(docname = as.numeric(docname)) %>% 
        rename(Article = docname) %>% # this seems to work better than including in above step
        left_join(
          spreadsheet_reduced, # CHECKING 12.29.20 - seems to have worked better than normal spreadsheet with corp_reduced
          by = "Article") %>% 
        select(-c(Text, Other_Metadata:Comp_Doc))

    }
```

## Explore various KWIC 

All of these keywords relate to claims made in ch. 2.

* primitiv

```{r}
primitiv_kwic <- 
  combine_kwic_with_data(corp, "primitiv*", 15)
```

* langweilig

```{r}
langweilig_kwic <- 
  combine_kwic_with_data(corp, c("langeweile", "langweilig*"), 10)
```

* proletarisch

```{r}
proletarisch_kwic <- 
  combine_kwic_with_data(corp, "proletarisch*", 10)
```

* pudowkin

```{r}
pudowkin_kwic <- 
  combine_kwic_with_data(corp, "pudowkin*", 10)
```

* kunst

```{r}
kunst_kwic <- 
  combine_kwic_with_data(corp, c("kunst", "künstler*"), 10)
```

* agitprop

```{r}
agitprop_kwic <- 
  combine_kwic_with_data(corp, "agitprop*", 10)
```

* bildung

```{r}
bildung_kwic <- 
  combine_kwic_with_data(corp, "bildung", 10)
```

* wissen

```{r}
wissen_kwic <- 
  combine_kwic_with_data(corp, "wissen*", 10)
```

* lehrstück MUTTER

```{r}
lehrstueck_mutter_kwic <- 
  combine_kwic_with_data(corp, "lehrstück*", 10) %>% 
  filter(Piece == "Mutter")
```

* Oratorium MASSNAHME

```{r}
oratorium_mass_kwic <- 
  combine_kwic_with_data(corp, "oratori*", 30) %>% 
  filter(Piece == "Massnahme")
```

* Arbeitersänger MASSNAHME

```{r}
arbeitersaenger_mass_kwic <- 
  combine_kwic_with_data(corp, "arbeitersänger*", 30) %>% 
  filter(Piece == "Massnahme")
```

* Stalin and Stalinismus

```{r}
combine_kwic_with_data(corp, "stalin*", 30) %>% 
  print()
```

Only 3 articles on Mutter.

* Cantata

```{r}
combine_kwic_with_data(corp, "Kantate*", 25) %>% 
  print()
```

No results.

### Special Case: LEHRLERN in Mother/Right

NB: Can't use FN, b/c can't specify valuetype
Here, adaptation of FN

1. create tibble

```{r}
lehrlern_kwic <- kwic(corp, dict_regex, window = 20, 
                      valuetype = "regex") %>% # must specify to used dict
  as_tibble()

lehrlern_kwic$docname <- lehrlern_kwic$docname %>% 
    str_replace("text", "") 

lehrlern_kwic <- lehrlern_kwic %>% mutate(docname = as.numeric(docname)) %>% 
    rename(Article = docname) %>% # this seems to work better than including in above step
    left_join(spreadsheet, by = "Article") %>% 
    select(-c(Text, Other_Metadata:Comp_Doc))
```

2. filter for Mutter & Right

```{r}
lehrlern_kwic_mutter_right <- lehrlern_kwic %>% 
  filter(Piece == "Mutter" & 
               Generalized_Political_Orientation == "Right")
```

### Combinations

langweilig + primitiv

```{r}
langweilig_primitiv_kwic <- 
  inner_join(langweilig_kwic, primitiv_kwic, by = "Article")
```

## Additional Terms Post-Processing (DFMs)

LEHRLERN in Mutter

```{r}
lehrlern_mutter_gpo_count <-  
  dfm_select(mutter_dfm_gpo, pattern = "LEHRLERN") %>% 
  as_tibble()

lehrlern_mutter_gpo_count
```


# Dates of Publication with Counts

## Create Tables

### General

All Articles

```{r}
dates_tib <- corp_reduced_datafr %>% 
  as_tibble() %>% 
  select(Article, Date, Piece) %>% 
  group_by(Piece, Date) %>% 
  count(Date) %>% 
  arrange(desc(n))
```

Separate Columns

```{r}
dates_tib_separate <- corp_reduced_datafr %>% 
  as_tibble() %>% 
    select(Article, Date, Piece) %>% 
    filter(str_detect(Date, "\\S{2}\\.\\S{2}\\.[:digit:]{4}")) %>% 
    separate(Date, sep = "\\.", into = c("day", "month", "year"))
```

Make Compatible with Lubridate

```{r}
dates_tib_lubridate <- dates_tib_separate %>% 
    mutate(day = as.numeric(day), 
           month = as.numeric(month),
           year = as.numeric(year)) %>%
    relocate(day, .after = month) %>% 
    relocate(year, .before = month) %>% 
    mutate(date = make_date(year, month, day)) %>% 
    select(Article, date, Piece) %>% 
  filter(!is.na(date)) %>% 
  arrange(date)
```

Percent of Articles WITHOUT Full Dates (i.e. excluded from lubridate)

```{r}
articles_perc_without_full_dates <- 
  (((nrow(dates_tib_separate) - 
     nrow(dates_tib_lubridate)) 
  / nrow(dates_tib_lubridate)) * 100) %>% 
  round() 
```

Percent of Articles WITH Full Dates (i.e. included for lubridate)

```{r}
articles_perc_with_full_dates <- 100 - articles_perc_without_full_dates
```


### By Piece

#### Measures Taken

All

```{r}
dates_mass <- dates_tib %>% 
  filter(Piece == "Massnahme") %>% 
  ungroup %>% 
  select(-Piece)
```

Edited, Lubridate

* Chronological, w/o counts - saved for computing range, length, etc.

```{r}
dates_mass_lubridate <- 
  dates_tib_lubridate %>% 
  filter(Piece == "Massnahme") %>% 
  arrange(date)
```


* Counted and Sorted Descending

```{r}
dates_tib_lubridate %>% 
  filter(Piece == "Massnahme") %>%
  count(date) %>% 
  arrange(desc(n))
```


#### Mother

All

```{r}
dates_mutter <- dates_tib %>% 
  filter(Piece == "Mutter") %>% 
  ungroup %>% 
  select(-Piece)
```

Edited, Lubridate

* Chronological, w/o counts - saved for computing range, length, etc.

```{r}
dates_mutter_lubridate <- 
  dates_tib_lubridate %>% 
  filter(Piece == "Mutter") %>% 
  arrange(date)
```

* Counted and Sorted Descending

```{r}
dates_tib_lubridate %>% 
  filter(Piece == "Mutter") %>%
  count(date) %>% 
  arrange(desc(n))
```

## Date Ranges, Time Lengths, etc.

### Time Length in YEARS

All Articles (Edited for Lubridate)

```{r}
difftime(tail(dates_tib_lubridate$date, 1),
         head(dates_tib_lubridate$date, 1)) %>% 
  time_length(unit = "year")
```

Measures Taken

```{r}
difftime(tail(dates_mass_lubridate$date, 1),
         head(dates_mass_lubridate$date, 1)) %>% 
  time_length(unit = "year")
```

Mother

```{r}
difftime(tail(dates_mutter_lubridate$date, 1),
         head(dates_mutter_lubridate$date, 1)) %>% 
  time_length(unit = "year")
```

### Range / Interval 

#### All

Save general start and end dates as variables for write-up:

```{r}
articles_first_date <- head(dates_tib_lubridate$date, 1)
articles_last_date <- tail(dates_tib_lubridate$date, 1)
```


General dates interval:

```{r}
interval(start = articles_first_date,
         end = articles_last_date)
```

#### Measures Taken

```{r}
interval(start = head(dates_mass_lubridate$date, 1),
         end = tail(dates_mass_lubridate$date, 1))
```

#### Mother

```{r}
interval(start = head(dates_mutter_lubridate$date, 1),
         end = tail(dates_mutter_lubridate$date, 1))
```

### Proportion of Articles near Premieres

#### Measures Taken

Save date of premiere as variable (cf. BFA 3: 431):

```{r}
mass_premiere_date <- ymd("1930-12-13")
```

Create interval for 1 week after premiere:

```{r}
mass_premiere_week <- interval(start = mass_premiere_date,
         end = mass_premiere_date + dweeks(x = 1))
```

Percentage of articles within 1 week of premiere:

```{r}
articles_mass_premiere_week_perc <- 
  round(((dates_mass_lubridate %>% 
    filter(date %within% mass_premiere_week) %>% 
    nrow()) / nrow(dates_mass_lubridate)) * 100)
```

#### Mother

Save date of premiere (cf. BFA 3: 478):

```{r}
mutter_premiere_date <- ymd("1932-01-17")
```

Create interval for 1 week after premiere:

```{r}
mutter_premiere_week <- interval(start = mutter_premiere_date,
         end = mutter_premiere_date + dweeks(x = 1))
```

Percentage of articles within 1 week of premiere:

```{r}
articles_mutter_premiere_week_perc <- 
  round(((dates_mutter_lubridate %>% 
    filter(date %within% mutter_premiere_week) %>% 
    nrow()) / nrow(dates_mutter_lubridate)) * 100)
```


## 1932 articles for Measures Taken

```{r}
dates_tib_lubridate %>% 
    filter(Piece == "Massnahme" &
            year(date) == 1932) %>% 
    left_join(spreadsheet)
```


# Visualizations

Create color scheme:

```{r}
colors_four <- c("#E41A1C", "#377EB8", "#4DAF4A", "#984EA3")
```


## English Labels

```{r}
labels_english <- c(Massnahme = "Measures Taken", Mutter = "Mother")
```

## Visual Summary of Reduced Corpus

Set-up for boxplot:

```{r}
# 3 steps for set up

# STEP 1
toks_grouped <- gen_datafr_reduced %>% 
    mutate(rowSums(.[ ,2:9102]), .after = 1) %>% 
    select(doc_id, `rowSums(.[, 2:9102])`) %>% 
    rename(tokens = `rowSums(.[, 2:9102])`)

# STEP 2
# add GPO column to gen_datafr_reduced
# can't combine with above for some reason
toks_grouped <- left_join(toks_grouped, 
                                    corp_reduced_datafr[ , c("doc_id",    "Generalized_Political_Orientation", "Piece")], 
                                    by = "doc_id", # 8.01 - now do this
                                    # by = c("document" = "doc_id"), # used to work
                                    copy = TRUE)

# STEP 3
# added for observation counts
toks_grouped <- toks_grouped %>% 
    add_count(Piece, Generalized_Political_Orientation)
```

Coding for boxplot:

```{r}
toks_summary_boxplot <- 
    toks_grouped %>% 
    ggplot(aes(x = Piece, y = tokens, 
               fill = Generalized_Political_Orientation)) +
    geom_boxplot(alpha = 0.7,
                 varwidth = TRUE) +
    stat_summary(fun = mean, geom="point", 
                 shape=21, size=5, color="black", fill="red", alpha = 0.75) +
    stat_summary(fun = mean, geom="line", 
                 size = 1.2, color = "red", alpha = 0.4, aes(group = 1)) +
    stat_summary(fun = median, geom="point", 
                 shape=21, size=5, color="black", fill="yellow", alpha = 0.75) +
    stat_summary(fun = median, geom="line", 
                 size = 1.2, color = "yellow", alpha = 0.4, aes(group = 1)) +
    scale_fill_brewer(type = "seq", palette = "Set1") +
    # geom_text()
    geom_jitter(color="darkgrey",
        size=1.25, alpha=0.95,
        show.legend = FALSE) + # may be too much
    coord_cartesian(xlim = NULL, ylim = c(0, 900)) +
    ylab("Tokens") +
  scale_x_discrete(labels=c("Measures Taken", "Mother")) +
    xlab(NULL) +
    labs(fill = "Political Orientation",
         title = "Tokens per Article (Post-Processing)",
         subtitle = "Scaled for readability. Several outliers excluded. Box width corresponds to number of articles.",
         caption = "Red and yellow points denote respecitively the mean and median tokens per article for each \n piece. NB: The positions of the scatter points do not correspond to political orientation.") +
    # below = text for number of articles in each category
    # # doesn't line up with variable box width
    # FIX BELOW - OBSERVATION COUNTS
    geom_text(aes(label = ..count.., 
                  y= ..prop..)
              , stat= "count",
              vjust = 1, # confusing - probably don't need
              position = position_dodge2(width = 0.5
                                          # c(0.4, 0.8)
                                        ) 
              ) +
  theme(axis.title.x = element_blank(),
          axis.ticks.x = element_blank(),
          panel.grid.major.x = element_blank(),
          panel.grid.major.y = element_line(color = "grey", linetype = 3),
          panel.grid.minor.y = element_line(color = "grey", linetype = 3),
          plot.caption.position = "plot",
          panel.background = element_rect(fill = "white", colour = 'black'))
# +
#     theme_bw()

toks_summary_boxplot
```

### Super Long Articles

The goal is to identify the long articles in *Measures - Unknown*, because they 
really stretch out the IQR in that category.

```{r}
corp_reduced_summary %>% 
    filter(Generalized_Political_Orientation == "Unknown" &
               Piece == "Massnahme") %>% 
    arrange(desc(tokens)) %>% 
  select(Article, tokens, Title:Piece)
```

## Wordclouds

Grouped by Piece:

```{r}
# must rename groups in English for word cloud
piece_dfm_no_erfurt_english <- dfm_group(piece_dfm_no_erfurt, groups = c("Measures Taken", "Mother"))

textplot_wordcloud(piece_dfm_no_erfurt_english,
                   max_words = 100,
                   color = colors_four,
                   rotation = FALSE,
                   comparison = TRUE,
                   labelcolor = "black")
```

*Mother* - Grouped by GPO (no unknown):

```{r}
wordcloud_mutter_gpo <- 
  textplot_wordcloud(mutter_dfm_gpo_no_unknown,
                   max_words = 100, # 125 or 100 is probably best
                   rotation = FALSE,
                   color = colors_four,
                   comparison = TRUE,
                   labelcolor = "black")

wordcloud_mutter_gpo
```


## Word Frequency 

By Piece:

```{r}
# grouped by piece (weighted)
freq_piece <- dfm_weight(gen_dfm_reduced, scheme = "prop") %>% # 12.21.20 applying dfm_weight seems to make no difference
    textstat_frequency(n = 15, groups = "Piece")

# good, except overlap of a couple of words, can't figure out how to fix
# yeah, but may not be necessary: keyness w/ target + reference is better,
# shows typicality rather than freq
freq_piece_plot <- 
  ggplot(freq_piece, 
       aes(x = nrow(freq_piece):1, y = frequency, fill = group)) +
    geom_col() +
    facet_wrap(~ group, scales = "free", nrow = 2,
               labeller = labeller(group = labels_english)
               ) +
    coord_flip() +
    scale_x_continuous(breaks = nrow(freq_piece):1, 
                       labels = freq_piece$feature) +
    labs(x = NULL, y = "Relative Frequency") +
    scale_fill_manual(values = colors_four) + # prob could just use brewer, b/c only 2
    theme_bw() +
    theme(legend.position = "none",
          panel.grid.major.y = element_line(color = "grey", linetype = 3),
          panel.grid.minor.y = element_blank(),
          panel.grid.major.x = element_line(color = "grey", linetype = 3),
          panel.grid.minor.x = element_line(color = "grey", linetype = 3),
          plot.caption.position = "plot",
          panel.background = element_rect(fill = "white", colour = 'black'))

freq_piece_plot
```

By Piece + GPO:

```{r}
freq_grouped_wt <- dfm_weight(gen_dfm_reduced, scheme = "prop") %>% 
    textstat_frequency(n = 10, 
                       groups = c("Piece", "Generalized_Political_Orientation")) 

freq_grouped_wt <- freq_grouped_wt %>% 
    mutate(group = str_replace_all(group, 
                                   c("Massnahme.Center" = 
                                       "Measures Taken | Center",
                                     "Massnahme.Left" = "Measures Taken | Left",
                                     "Massnahme.Right" = 
                                       "Measures Taken | Right",
                                     "Massnahme.Unknown" = 
                                       "Measures Taken | Unknown",
                                     "Mutter.Center" = "Mother | Center",
                                     "Mutter.Left" = "Mother | Left",
                                     "Mutter.Right" = "Mother | Right",
                                     "Mutter.Unknown" = "Mother | Unknown")))

# good but would want to rearrange cols
# currently: C - L - R - U
freq_piece_gpo_plot <- ggplot(freq_grouped_wt, 
       aes(x = nrow(freq_grouped_wt):1, y = frequency, fill = group)) +
    geom_col() +
    facet_wrap(~ group, scales = "free", nrow = 2,
               # labeller = labeller(group = labels_english
               ) +
    coord_flip() +
    scale_x_continuous(breaks = nrow(freq_grouped_wt):1, 
                       labels = freq_grouped_wt$feature) +
    labs(x = NULL, y = "Relative Frequency") +
    scale_fill_manual(values = c(colors_four, colors_four)) + # repeat b/c need 8
    theme_bw() +
    theme(legend.position = "none",
          panel.grid.major.y = element_line(color = "grey", linetype = 3),
          panel.grid.minor.y = element_blank(),
          panel.grid.major.x = element_line(color = "grey", linetype = 3),
          panel.grid.minor.x = element_line(color = "grey", linetype = 3),
          plot.caption.position = "plot",
          panel.background = element_rect(fill = "white", colour = 'black'))

freq_piece_gpo_plot
```

## Correspondence Analysis


Main

```{r}
ca_main_english <- plot(grouped_ca_no_erfurt_or_unknown_english,
                invisible = "row",
                col.quali.sup = "darkblue",
                selectCol = "contrib 20",
                autoLab = "y", # "n" worked decently for Massnahme but terrible for Mutter
                # xlim = c(-1.75, 1.25), # didn't help much - default is -1.5, 1.5
                ylim = c(-0.75, 1.75), # second modified sizing - probably better
                # ylim = c(-1, 2), # first modified sizing
                unselect = 1,
                cex = 0.85)

ca_main_english <- ca_main_english + 
    labs(title = "The Political-Aesthetic Space of The Measures Taken and The Mother",
         subtitle = "(CA of pieces and political orientations with the top 20 contributing keywords.)") +
    theme_bw()

ca_main_english
```

Measures

```{r}
ca_measures <- plot(grouped_ca_no_erfurt_or_unknown_english,
     invisible = "row",
     col.quali.sup = "darkblue",
     selectCol = "contrib 20",
     autoLab = "y",
     xlim = c(0, 1.5),
     ylim = c(-1, 2), 
     unselect = 1,
     cex = 0.85)

ca_measures <- ca_measures + 
  labs(title = "The Political-Aesthetic Space of The Measures Taken",
       subtitle = "(Enlargement of positive x region of above.)") +
  theme_bw()

ca_measures
```

Mother

```{r}
ca_mother <- plot(grouped_ca_no_erfurt_or_unknown_english,
     invisible = "row",
     col.quali.sup = "darkblue",
     selectCol = "contrib 20",
     autoLab = "y",
     xlim = c(-1.25, 0),
     ylim = c(-0.75, 0.25), 
     unselect = 1,
     cex = 0.85)

ca_mother <- ca_mother + 
  labs(title = "The Political-Aesthetic Space of The Mother",
       subtitle = "(Enlargement of negative x region of above.)") +
  theme_bw() 

ca_mother
```



